### 2018-01-26 includes/problems.tex
small updates from Dmitry's comments

    \begin{table}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name} & \textbf{Seed}                            & \textbf{Qunatity} \\ \hline
        Amazon        & Two industrial regex membership problems & 516\\ \hline
        Regex         & Z3str2 regular expression test suite     & 10,577\\ \hline
    \end{tabular}
    \caption{\transformer{} generated problem sets.}
    \label{tbl:transformed}
    \end{table}

    The first category, labeled Amazon, started as two seed files.
    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
    \todo{Can I say something like that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
    In total, 516 unique problems were generated from these two seeds.

    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} 
    \todo{Is this right? If so where we can cite?}. 
    This test suite contains 42 problems dealing with a wide variety of regular expressions.
    Through cumulative transformations, as before, we were able to produce 10,577 unique benchmarks.

>>>>

    \begin{table}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name} & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
        Amazon        & Two industrial regex membership problems & 516\\ \hline
        Regex         & Z3str2 regular expression test suite     & 10,577\\ \hline
    \end{tabular}
    \caption{\transformer{} generated problem sets.}
    \label{tbl:transformed}
    \end{table}

    The first category, labeled Amazon, started as two seed files.
    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
    Both problems come from our industrial collaborators. 
    In total, 516 unique problems were generated from these two seeds.

    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{z3str2-tests}.
    This test suite contains 42 problems dealing with a wide variety of regular expressions.
    Through cumulative transformations, as before, we were able to produce 10,577 unique benchmarks.
